Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-13 article.qmd
Add biomodels reference

Several commonly used reactions are predefined as `MassAction` subclasses,
such as
`MichaelisMenten` ($S + E \rightarrow ES -> P + E$)
and its approximate form without the intermediate species $ES$,
and it is also simple to implement your own as subclasses of `Reaction` or `MassAction`.
Additionally, SimBio supports importing from and exporting to SBML,
and downloading them directly from BioModels (@fig-simbio-io).

@@

To evaluate SimBio's reproducibility,
we analyzed curated SBML models from BioModels (ref needed).
Among the first 100 curated models from BioModels we selected 60 which did not contains events,
as SimBio doesn't support events yet.
We simulated the selected models with COPASI
and used the simulated results as ground truth,
and demonstrated that SimBio reproduces the results with minor numerical differences depending on the solver tolerance.

>>>>

Several commonly used reactions are predefined as `MassAction` subclasses,
such as
`MichaelisMenten` ($S + E \rightarrow ES -> P + E$)
and its approximate form without the intermediate species $ES$,
and it is also simple to implement your own as subclasses of `Reaction` or `MassAction`.
Additionally, SimBio supports importing from and exporting to SBML,
and downloading them directly from BioModels [@malik-sheriffBioModels15Years2020] (@fig-simbio-io).

@@

To evaluate SimBio's reproducibility,
we analyzed curated SBML models from BioModels [@malik-sheriffBioModels15Years2020].
Among the first 100 curated models from BioModels we selected 60 which did not contains events,
as SimBio doesn't support events yet.
We simulated the selected models with COPASI
and used the simulated results as ground truth,
and demonstrated that SimBio reproduces the results with minor numerical differences depending on the solver tolerance.
